\documentclass[a4paper,10pt]{article}
\usepackage[margin=2.5cm, nohead]{geometry}
\usepackage{palatino, url, multicol}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage[english]{babel}

\title{Group report for AP2DX of week 4}
\author{Maarten de Waard}
\date{27$^{th}$ of June - 1$^{st}$ of Juli}

\begin{document}
\maketitle

\section*{Group members}
\noindent Maarten Inja \textit{(Leader)}\\
Maarten de Waard \textit{(Secretary)}\\
Jasper Timmer\\
Wadie Assal\\

\section*{The week}
\subsection*{Monday}
Monday we started by evaluating our draft report. Most of it was fine, although there were some things we could have elaberated on a bit more. After evaluating we started programming again. 

The Maartens started on the mapper, while Jasper and Wadie started programming our movement algorithm.
The mapper would be an external program, ``DP Slam''. This was a program, programmed in C. 

\subsection*{Tuesday}
This day the Maartens continued on getting the Mapper to work. The java programs
to be able to run DP-slam from our code and to be able to interpret the images
it creates were made (\texttt{PictureViewer.java} and \texttt{Slammer.java}).
Especially getting the program to work on windows was hard.

Jasper and Wadie continued perfecting their movement algorithm. 

\subsection*{Wednesday}
This day we finished the movement algorithm. Unfortunately Jasper was done with
this around 2 in the night, and forgot to push his code. We found this out the
evening after, after the demonstration was done. 

We also got the code for the mapper working, but only on linux. On a windows
system, the mapper simply only forwards messages to the Planner. Since our
system is distributed, it is no problem to start the mapper on another computer,
than all the other programs.

\subsection*{Thursday}
We had to do our presentation this morning. Jasper and Maarten did the
presentation, and that went pretty well. As a matter of fact, if we were to do
the course ``Portfolio'', we would have gotten an eight for it!

Wadie and Maarten then presented our demo, with the code of Wednesday afternoon,
because Jasper forgot to push. This still went okay, but the navigation could have been better.

\subsection*{Friday}
On Friday we finished everything.
\end{document}
